Informative Autonomous Sampling of Oceanographic Variables Using Joint Excursion Sets

### 2020-04-23 ans_to_reviewers/answers-to-reviewers.tex

\item[3.1.1] General: The inferential problem considered is the paper is that of estimating the “boundary”
of a plume. However, the authors never define exactly what a “boundary” is. Such a definition
should be provided, as well as some discussion of why determining the location of a boundary
is so important. Why is it not sufficient to create a map of predictions (with an accompanying
map of prediction error variances) for the variable(s) under study throughout the region of
interest (a problem for which there is a huge literature on sampling design)?\par
\action: Our actions
\vspace{1em}

\item[3.1.2] Page 8, second paragraph of Section 4.1: The assumptions of separability and isotropy, and even stationarity, are not really necessary for the methodological development of Sections 4–6.
I suggest that you wait to make these assumptions until you get to the simulation studies and
example.\par
\action: Our actions
\vspace{1em}

\item[3.1.3] Page 9, second paragraph of Section 4.2: It has been assumed here that the measurement
errors for temperature and salinity at any given location are uncorrelated. Is this a reasonable
assumption? This could easily be checked by taking replicate measurements at each site.\par
\action: Our actions
\vspace{1em}

\item[3.1.4] General: Related to the previous point, I do not understand why sampling locations are being restricted to a regular grid. In fact, it seems unwise because it is well known (see, for example, Chapters 9 and 22 of Handbook of Environmental and Ecological Statistics, 2019, CRC Press)
that the quality of inferences for spatial fields can be improved substantially by taking some
observations very close to others.\par
\action: The AUV and the sampling happens regularly at 1 Hz, the collected measurements are then assimilated to this regular grid. The sampling density is therefore higher than the grid resolution. Still, there is a limitation on restricting the sampling locations to finite number of fixed locations. However, in order to handle the computational load and resources available on the AUV this simplification is necessary. % Comment Trygve: Should we add some more here? 
\vspace{1em}

### 2020-04-29 main_new.tex
updates
Updated missing commands

% put your definitions there:
\startlocaldefs
\endlocaldefs

@@

\begin{aug}
\author{\fnms{Trygve Olav} \snm{Fossum}\thanksref{t1,t2}, \corref{} \ead[label=e1]{trygve.o.fossum@ntnu.no}}
\author{\fnms{Jo} \snm{Eidsvik}\thanksref{t3}, \ead[label=e2]{jo.eidsvik@math.ntnu.no}}
\author{\fnms{David} \snm{Ginsbourger}\thanksref{t4}, \ead[label=e3]{david.ginsbourger@idiap.ch}}
\and
\author{\fnms{Kanna} \snm{Rajan}\thanksref{t2,t5,t6}. \ead[label=e4]{kanna.rajan@ntnu.no}}

\affiliation[t1]{Department of Marine Technology, The Norwegian University of Science and Technology (NTNU), Trondheim, Norway.} 
\affiliation[t2]{Centre for Autonomous Marine Operations and Systems (AMOS).}
\affiliation[t3]{Department of Mathematical Sciences, NTNU.}
\affiliation[t4]{Uncertainty Quantification and Optimal Design group, Idiap Research Institute, Martigny, Switzerland.}
\affiliation[t5]{Department of Engineering Cybernetics, NTNU}
\affiliation[t6]{Underwater Systems and Technology Laboratory, Faculty of Engineering, University of Porto, Portugal.}

\address{\\Trygve Olav Fossum \\Department of Marine Technology\\ Otto Nielsens veg. 10, 7491 Trondheim\\ Norway\\
\printead{e1}}
\address{Jo Eidsvik\\Department of Mathematical Sciences\\ Hogskoleringen 1, 7491 Trondheim\\ Norway\\ \printead{e2}}
\address{David Ginsbourger\\ Idiap Research Institute\\ Rue Marconi 19, 1920 Martigny\\ Switzerland\\
\printead{e3}}
\address{Kanna Rajan\\Department of Engineering Cybernetics\\ O. S. Bragstads Plass 2D, 7034 Trondheim\\ Norway\\
\printead{e4}}

>>>>

% put your definitions there:
\startlocaldefs
\newcommand{\edcomment}[1]{{\color{green}{\{Editor: #1\}}}}
\newcommand{\frevcomment}[1]{{\color{blue}{\{Rev 1: #1\}}}}
\newcommand{\srevcomment}[1]{{\color{red}{\{Rev 2: #1\}}}}
\newcommand{\trevcomment}[1]{{\color{violet}{\{Rev 3: #1\}}}}
\endlocaldefs

@@

\begin{aug}
\author{\fnms{Trygve Olav} \snm{Fossum}\thanksref{t1,t2}, \corref{} \ead[label=e1]{trygve.o.fossum@ntnu.no}}
\author{\fnms{Jo} \snm{Eidsvik}\thanksref{t3}, \ead[label=e2]{jo.eidsvik@math.ntnu.no}}
\author{\fnms{David} \snm{Ginsbourger}\thanksref{t4}, \ead[label=e3]{david.ginsbourger@idiap.ch}}
\and
\author{\fnms{Kanna} \snm{Rajan}\thanksref{t5}. \ead[label=e4]{kanna.rajan@fe.up.pt}}

\affiliation[t1]{Department of Marine Technology, The Norwegian University of Science and Technology (NTNU), Trondheim, Norway.} 
\affiliation[t2]{Centre for Autonomous Marine Operations and Systems (AMOS).}
\affiliation[t3]{Department of Mathematical Sciences, NTNU.}
\affiliation[t4]{Uncertainty Quantification and Optimal Design group, Idiap Research Institute, Martigny, Switzerland.}
% \affiliation[t5]{Department of Engineering Cybernetics, NTNU}
\affiliation[t5]{Underwater Systems and Technology Laboratory, Faculty of Engineering, University of Porto, Portugal.}

\address{\\Trygve Olav Fossum \\Department of Marine Technology\\ Otto Nielsens veg. 10, 7491 Trondheim\\ Norway\\
\printead{e1}}
\address{Jo Eidsvik\\Department of Mathematical Sciences\\ Hogskoleringen 1, 7491 Trondheim\\ Norway\\ \printead{e2}}
\address{David Ginsbourger\\ Idiap Research Institute\\ Rue Marconi 19, 1920 Martigny\\ Switzerland\\
\printead{e3}}
\address{Kanna Rajan\\Underwater Systems and Technology Laboratory,
  Faculty of Engineering,\\ Rua Dr. Roberto Frias\\ University of Porto, Portugal\\
% Department of Engineering Cybernetics\\ O. S. Bragstads Plass 2D, 7034 Trondheim\\ Norway\\
\printead{e4}}
